### 2017-02-01 CO750-ApproximationAlgorithmsTopics/assignments/assignment_01.tex
p4

Let $G = (V,E)$ be a graph with edge costs $c: E \rightarrow \R_+$. Let $r \in V$ be a root vertex. Let $R \subseteq V \backslash \{r\}$ be a set of terminals. Let $d_v \in \{2^0, 2^1, \dots, 2^\delta\}$ denote the demand of $v$ for each $v \in R$. We assume we have an $O(1)$-approximation algorithm for the Steiner Tree problem. Then each iteration of step $2$ of the given algorithm runs in polynomial time using the assumed approximation algorithm. There are $\delta+1$ iterations of step $2$ which is $O(\log \max_v d_v)$ and hence polynomial in the number of bits needed to specify the input to the problem. Thus the entirety of step $2$ runs in polynomial time and hence the given algorithm runs in polynomial time. It is clear the tree returned spans $R \cup \{r\}$ since the partial solution at each iteration $i$ spans $R_\delta \cup \dots \cupR_i \cup \{r\}$. Further at each iteration $i$ the paths in the final solution connecting $v \in R_i$ to $r$ are assigned costs $2^i$ on their edges and hence a feasible flow of value $d_v$ from $r$ to $v$ is possible. Thus the algorithm returns a feasible solution in polynomial time.

@@

It remains to verify the approximation factor of $O(1)$. We do so by induction on the number of iterations the algorithm needs to run to return a solution.

>>>>

Let $G = (V,E)$ be a graph with edge costs $c: E \rightarrow \R_+$. Let $r \in V$ be a root vertex. Let $R \subseteq V \backslash \{r\}$ be a set of terminals. Let $d_v \in \{2^0, 2^1, \dots, 2^\delta\}$ denote the demand of $v$ for each $v \in R$. We assume we have an $O(1)$-approximation algorithm for the Steiner Tree problem. Then each iteration of step $2$ of the given algorithm runs in polynomial time using the assumed approximation algorithm. There are $\delta+1$ iterations of step $2$ which is $O(\log \max_v d_v)$ and hence polynomial in the number of bits needed to specify the input to the problem. Thus the entirety of step $2$ runs in polynomial time and hence the given algorithm runs in polynomial time. It is clear the tree returned spans $R \cup \{r\}$ since the partial solution at each iteration $i$ spans $R_\delta \cup \dots \cup R_i \cup \{r\}$. Further at each iteration $i$ the paths in the final solution connecting $v \in R_i$ to $r$ are assigned costs $2^i$ on their edges and hence a feasible flow of value $d_v$ from $r$ to $v$ is possible. Thus the algorithm returns a feasible solution in polynomial time.

@@

It remains to verify the approximation factor of $O(1)$. We do so by induction on the number of iterations the algorithm needs to run to return a solution. In the base case, that is when $\delta = 0$, the algorithm returns an $O(1)$-approximate Steiner Tree connecting $R \cup \{r\}$ and installs capacity of $1$ on each edge. By observing that the optimal solution in this case is a Steiner Tree connecting $R \cup \{r\}$ with capacity $1$ on each edge we see that the approximation factor holds in this case.
Suppose that $\delta > 0$ and for any problem instance with maximum demand $2^{\alpha}$ with $0 \leq \alpha < \delta$ the algorithm returns an $O(1)$ approximate solution. We will describe solutions by an ordered pair $(T, x)$ where $T$ is a tree and $x : T \rightarrow \R_+$ maps edges of $T$ with their corresponding capacity. Then the objective function, which we denote by $f$, in our problem maps feasible solutions $(T,x)$ as follows:
$$f(T,x) = \sum_{e \in T} c_e x_e.$$
Let $(T,x)$ be the solution returned by running our algorithm, and let $(T^*, x^*)$ be the optimal solution. Let $T_{\delta}$ be the $O(1)$-approximate Steiner Tree connecting $R_\delta \cup \{r\}$ in the first iteration (iteration $\delta$) of our algorithm. Let $\bar{T}$ denote the solution returned by our algorithm running on the residual problem with input graph $G_{\delta-1}$	
